Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-30 lloveras_2020.tex
Version Final

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. \\
In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines. For each field line leg, the results were then fit to Equations \ref{Nfit} and \ref{Tfit}{, considering only data points above heliocentric height $1.055\,\mrsun$. We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.  Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}

@@

@@

\begin{acks}
D.G.Ll. and C.M.C. {acknowledge} CONICET doctoral {fellowships} (Res. Nr. 4870) to IAFE that supported {their} participation in this research. {D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}

>>>>

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines. For each field line leg, the results were then fit to Equations \ref{Nfit} and \ref{Tfit}{, considering only data points above heliocentric height $1.055\,\mrsun$. We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.  Legs of type 0 are not included for AWSoM as it currently can not simulate down loops, as discussed in Section \ref{discu}.}

@@

Down loops are to be expected if heating is enhanced at the footpoints of coronal structures. \citet{schiff_2016} numerically simulated stable down loops by means of a 1D steady-state model, requiring that the initial population of Alfvén waves is efficiently converted into compressive modes. Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT analysis \citep{nuevo_2013}. In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient. So far, attempts to reproduce observed down loops in AWSoM simulations by increasing the reflection coefficient have not been successful.

@@

\begin{acks}
D.G.L. and C.M.C. {acknowledge} CONICET doctoral {fellowships} (Res. Nr. 4870) to IAFE that supported {their} participation in this research. {D.G.L, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant 20020160100072BA to DCAO-UBA to FCEyN-UBA and IAFE that partially supported his participation in this research.} W.M. and B.v.H acknowledge NSF grant 1663800 that partially supported his participation in this research. W.M. also acknowledges NASA grants NNX16AL12G and 80NSSC17K0686.
\end{acks}

### 2020-01-30 lloveras_2020_Albert.tex
Version Final

\albert{Down loops are to be expected if heating is enhanced at the footpoints of coronal structures. \citet{schiff_2016} numerically simulated stable down loops by means of a 1D steady-state model, requiring that the initial population of Alfvén waves is efficiently converted into compressive modes. Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT analysis \citep{nuevo_2013}. In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient. So far, attempts to reproduce observed down loops in AWSoM simulations by increasing the reflection coefficient have not been successful.}

>>>>

\albert{Down loops are to be expected if heating is enhanced at the footpoints of coronal structures. \citet{schiff_2016} reproduced down loops by means of numerical simulations based on a 1D steady-state model, by requiring that the initial population of Alfvén waves is efficiently converted into compressive modes. Mode conversion is favored by the $\beta\gtrsim 1 $ condition found to characterize the regions where down loops are observed in DEMT \citep{nuevo_2013}. In the AWSoM model, heating is controlled by two key parameters, namely, the Alfvén wave dissipation length, and its reflection coefficient. So far, attempts to reproduce down loops within AWSoM simulations by increasing the reflection coefficient have not been successful.}
